Some examples in extended logic counting classes

### 2015-08-04 tex/examples.tex
1 ago

 \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm} 
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}

\def\dotminus{\mathbin{\ooalign{\hss\raise1ex\hbox{.}\hss\cr
  \mathsurround=0pt$-$}}}

\def\Eone{\#\Sigma_1\textsc{[FO]}}
\def\Etwo{\#\Pi_1\textsc{[FO]-HORN}}
\def\Ethree{\#\Sigma_2\textsc{[FO]-HORN}}
\def\Efour{\#\Pi_2\textsc{[FO]-HORN}}

\def\Truc{\textsc{Struct}[\L]}

\def\A{{\frak A}}
\def\C{{\cal C}}
\def\F{{\cal F}}
\def\L{{\cal L}}
\def\N{\mathbb{N}}
\def\P{\vec{P}}
\def\R{\vec{R}}
\def\S{\vec{S}}
\def\X{\vec{X}}
\def\Y{\vec{Y}}
\def\Z{\vec{Z}}
%% a - arity of \X / arity of assignments \P to \X
%% b - arity of predicates in \S
%% c - arity of auxiliar predicates/variables
\def\c{\vec{c}} %% super auxiliar elements
\def\d{\vec{d}} %% counted elements
\def\e{\vec{e}} %% counted elements
%% f - counting function
%% g - other functions
%% h - other functions
%% i - index
%% j - index
%% k - emergency index / size of tuple
%% l - emergency index / size of tuple
\def\l{\vec{\ell}}
%% m - size of variable tuple
%% n - size of predicate tuple
%% o - not used
%% p - 
%% q - 
%% r - size of \X / \P
\def\s{\vec{s}}
%% t - size of \S
\def\t{\vec{t}}
\def\u{\vec{u}} %% auxiliary variables
\def\v{\vec{v}} %% auxiliary variables
\def\w{\vec{w}} %% auxiliary variables
\def\x{\vec{x}} %% quantified variables
\def\y{\vec{y}} %% auxiliary variables
\def\z{\vec{z}} %% open variables
\def\ep{\vec{o}}
\def\ga{\vec{p}}

\newtheorem{theo}{Theorem}
\newtheorem{lemma}[theo]{Lemma}
\newtheorem{claim}[theo]{Claim}
\newtheorem{coro}[theo]{Corollary}

\title{Some examples in extended logic counting classes}

\begin{document}
\maketitle

\section{{\sc \#3-DNF}}
A function $f:\Truc \to \N$ is in $\Eone$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\Y,\y)$ such that $f = f_{\varphi(\Y,\y)}$. We will now show that {\sc \#3-DNF} $\in\Eone$.\\

@@

\section{{\sc \#3-HORN-SAT}}
A function $f:\Truc \to \N$ is in $\Etwo$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x,\Y,\y)$ such that $f = f_{\forall \x\,\varphi(\x,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#3-HORN-SAT} $\in\Etwo$.\\

@@

\section{{\sc \#DNF}}
A function $f:\Truc \to \N$ is in $\Ethree$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x^1,\x^2,\Y,\y)$ such that $f = f_{\exists\x^1\forall \x^2\,\varphi(\x^1,\x^2,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#DNF} $\in\Ethree$.

@@

\end{document}

>>>>

\section{Some examples in extended logic counting classes}

\subsection{{\sc \#3-DNF}}
A function $f:\Truc \to \N$ is in $\Eone$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\Y,\y)$ such that $f = f_{\varphi(\Y,\y)}$. We will now show that {\sc \#3-DNF} $\in\Eone$.\\

@@

\subsection{{\sc \#3-HORN-SAT}}
A function $f:\Truc \to \N$ is in $\Etwo$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x,\Y,\y)$ such that $f = f_{\forall \x\,\varphi(\x,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#3-HORN-SAT} $\in\Etwo$.\\

@@

\subsection{{\sc \#DNF}}
A function $f:\Truc \to \N$ is in $\Ethree$ if there exists an {\sc FO}-extended quantifier-free $\L$-formula $\varphi(\x^1,\x^2,\Y,\y)$ such that $f = f_{\exists\x^1\forall \x^2\,\varphi(\x^1,\x^2,\Y,\y)}$ and any second order variables only appear in Horn clauses. We will now show that {\sc \#DNF} $\in\Ethree$.

@@
